Distributed Tic Tac Toe:\\ Peer-to-Peer Team-Based Gaming System

### 2017-11-20 paper/paper.tex
Fixed a small bug and added a reference

Distributed software requires a new look on the system – the number of devices
has gone up and with it so have the number of processes, concerns and complexities.
Some concepts have now changed and need to be dealt with differently; One such
example if this would be mutual exclusion. We believe programs that serve as examples and
focus on simple local tasks turned into distributed ones can help many people
trying to make this step with a hands-on experience of what they are preparing
for. Seeing theory in practice is a proven technique and there is evidence for
this in every university course that features practical work. This is especially
true where games are concerned, proving to be an effective means of communicating 
programming methods and techniques in an engaging way \cite{3}. For this reason, 
the team has decided to take a simple, well known game and develop it into a distributed 
system; Tic Tac Toe played as a peer-to-peer, team-based gaming system where the players are organised into teams and required to vote on moves for their team.

>>>>

Distributed software requires a new look on the system – the number of devices
has gone up and with it so have the number of processes, concerns and complexities.
Some concepts have now changed and need to be dealt with differently; One such
example if this would be mutual exclusion. We believe programs that serve as examples and
focus on simple local tasks turned into distributed ones can help many people
trying to make this step with a hands-on experience of what they are preparing
for. Seeing theory in practice is a proven technique and there is evidence for
this in every university course that features practical work. This is especially
true where games are concerned, proving to be an effective means of communicating 
programming methods and techniques in an engaging way
\cite{Kiniry:2011:VG:1984674.1984681}. For this reason, the team has decided to
take a simple, well known game and develop it into a distributed system; Tic Tac
Toe played as a peer-to-peer, team-based gaming system where the players are
organised into teams and required to vote on moves for their team.
